Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-07 doc/report/msc-report.tex
doc/report/msc-report.tex: * added \chapterquote and quotes in the beginning of each chapter. * altered flow in Dimension section.

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

\begin{document}
\maketitle

\noindent \Large{\textbf{Abstract}}
\vspace{12pt}

@@

\tableofcontents
\vfill
\pagebreak

@@

% TODO: den har texten passar battre i ett eget stycke/sektion, background reading style.
Says Wikipedia: "Data warehouse is a repository of an organization's electronically stored data. Data warehouses are designed to facilitate reporting and analysis." The main actions of a data warehouse is extract, transform and load data, although not necessarily in that order.

@@

@@

A data cube is a conceptual n-dimensional array of values. The values are
numerical facts belonging to some dimension. The data cube is also known as a
hypercube. The data cube relates to multidimensional analogues of squares and cubes.
In this context, each dimension of the cube corresponds to an attribute of
the data in question and each point along the dimension's axis is a value of
the corresponding attribute. The mental model of a data cube aids in
reasoning about dimensions. Data cubes are traditionally modeled as star
schemas in relational database systems. \cite{olap_solutions}

@@

@@

@@

@@

@@

@@

>>>>

\author{Per Andersson, Fredrik M{\"o}llerstrand}

\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

\newcommand{\chapterquote}[2] {
\begin{quote}
\textit{"{#1}"}

--- {#2}
\end{quote}

\vspace{24pt}
}

\begin{document}

\maketitle

\noindent \Large{\textbf{Abstract}}

\vspace{12pt}

@@

\tableofcontents

\vfill

@@

% TODO: den har texten passar battre i ett eget stycke/sektion, background reading style.

\chapterquote{Data warehouse is a repository of an organization's
electronically stored data. Data warehouses are designed to facilitate
reporting and analysis.}{Wikipedia}

The main actions of a data warehouse is extract, transform and load data,
although not necessarily in that order.

@@

\chapterquote{Einstein explained his theory to me every day, and on my
arrival I was fully convinced that he understood it.}{Chaim Weizmann}

@@

A data cube is a conceptual n-dimensional array of values, in which the values
are numerical facts belonging to some dimension. The data cube is also known as
a hypercube, relating to multidimensional analogues of squares and cubes. In
this context, each dimension of the cube corresponds to an attribute of the
data in question and each point along the dimension's axis is a value of the
corresponding attribute. The mental model of a data cube aids in reasoning
about dimensions. Data cubes are traditionally modeled as star schemas in
relational database systems. \cite{olap_solutions}

@@

\chapterquote{Arrange whatever pieces come your way.}{Virgina Wolf}

%\chapterquote{In short, intelligence, considered in what seems to be its
%original feature, is the faculty of manufacturing artificial objects,
%especially tools to make tools, and of indefinitely urging the
%manufacture.}{Henri Bergson}

@@

%\chapterquote{A good idea is about ten percent and implementation and hard
%work, and luck is 90 percent.}{Guy Kawasaki}

\chapterquote{It is not always what we know or analyzed before we make a
decision that makes it a great decision. It is what we do after we make the
decision to implement and execute it that makes it a good
decision.}{William Pollard}

@@

\chapterquote{There comes a time when all people break down and do the
unthinkable: They read the manual.}{Unknown}

@@

\chapterquote{Example is not the main thing in influencing others, it's
the only thing}{Albert Schweitzer}

%\chapterquote{There is nothing so annoying as a good example!!}{Mark Twain}

%\chapterquote{Example isn't another way to teach, it is the only way to
%teach}{Albert Einstein}

@@

\chapterquote{In discussion comes the light!}{Unknown}

@@

\chapterquote{When we can't dream any longer we die.}{Emma Goldman}
